Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar

### 2018-10-16 archive/accessPEP3.Rmd
Reorganizing files and creating draft rmd to push to googledrive

### Preliminary data from Madagascar Clinics
* Commune level average travel time to the closest CTAR (generated from global travel time layer from Malaria Atlas Project).
* Human population per commune extracted from World Pop
* 16 months of data on reported animal bites from the Moramanga District in Madagascar 
* In the next month, we will have 4 years of data on reported animal bites from 20 of the 31 CTAR.

```{r setup, echo = FALSE, message = FALSE, results = 'hide'}
## Clean-up
## Packages
# for gis 
library(knitr)
library(raster)
library(maptools)
library(maps)
library(GISTools)
library(rgdal)
library(sp)
library(rgdal)
library(gdistance)
# everything else
library(lubridate)
library(reshape2)
library(tidyverse)
library(rjags)
library(coda)
library(lattice)
# pkgs <- c("lattice", "coda")
# require(pkgs, character.only = TRUE)

## gis data {NEED TO FIGURE OUT PROJECTIONS!}
p4s <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"
mada.district <- readOGR("data/MadaGIS/MadaPops.shp", p4s = p4s)
ctar.gps <- read.csv("data/ctar_gps.csv")
ctar.gps <- SpatialPoints(cbind(ctar.gps$LONGITUDE, ctar.gps$LATITUDE),
                          proj4string = crs(mada.district))
ctar.atts <- readOGR("data/MadaGIS/31CTAR.shp")
# ## getting travel time layer
mada.access <- raster("output/study.area.accessibility.tif")
mada.access <- mask(mada.access, mada.district)
plot(mada.access/60, breaks = c(0, 1, 2, 3, 4, 5, 6, 8, 16, max(values(mada.access)/60, na.rm = TRUE)),
     col = c("#fff7f3", "#fde0dd", "#fcc5c0", "#fa9fb5", "#f768a1", "#dd3497", "#ae017e", "#7a0177", "#49006a"))
#col = colorRampPalette(c("navyblue", "mediumturquoise", "orange", "red"))(11), axes = FALSE, box = FALSE)
points(ctar.gps, pch = 18, col = "grey", cex = 1)

## getting which districts have a ctar
mada.district$ctar.in <- ifelse(is.na(match(mada.district$district, ctar.atts$District)), 0, 1)
mada.district$ctar.in[mada.district$district %in% c('Manakara Atsimo', 'Toliary-I', 'Taolagnaro',
                                                    'Nosy-Be', "Ambovombe-Androy")] <- 1

## should equal 31
sum(mada.district$ctar.in)

## mid.pops
mada.district$midpops <- (mada.district$pop2015adj + mada.district$pop2020adj)/2

## ctar data: getting exposure matrix (district by year)
ctar.data <- read.csv("data/SaisieRage_DATA_2018-06-28_0956.csv")
ctar.data %>% 
  filter(type != "contact") %>% # exclude contacts
  mutate_at(vars(starts_with("date")), funs(mdy(.))) %>% # format dates
  group_by(year = year(date_de_consultation), district) %>% # group by year and district
  summarize(n = n()) -> exposures # get count of exposures

## merge district shapefile with the summarized matrix!
exposure.mat <- dcast(exposures, district ~ year)
colnames(exposure.mat) <- c("district", "year2013", "year2014", "year2015", "year2016", "year2017", "year2018")
mada.district@data <- merge(mada.district@data, exposure.mat, by.x = "mdg_dis_co", by.y = "district", all.x = TRUE)
vars <- c("mdg_dis_co", "district", "midpops", "study_area", "ctar.in",
          "year2014", "year2015", "year2016", "year2017")

## Getting all dist data
mada.district@data %>%
  select(!!vars) %>%
  mutate_at(vars(starts_with("year")), funs(replace(., is.na(.), 0))) %>%
  mutate(avg.bites100k = (select(., starts_with("year")) %>% rowSums())/4/(midpops/1e5),
         dogs_min = round(midpops/25), dogs_max = round(midpops/5)) -> dist.data

## districts that are non-reporter and data not available yet CTAR
no_data <- c("Manja", 'Ambatondrazaka', "Vangaindrano", "Tsiroanomandidy",
             "Antsiranana I", "Taolagnaro", "Ambovombe-Androy", "Nosy-Be", "Ambatomainty",
             "Marolambo", "Sainte-Marie", "Antananarivo Renivohitra", "Antananarivo Avaradrano", 
             "Ambohidratrimo", "Ankazobe", "Manjakandriana", "Anjozorobe", "Andramasina", 
             "Antananarivo Atsimondrano", "Fianarantsoa I", "Ambalavao", "Ambohimahasoa", 
             "Ikalamavony", "Lalangina", "Vohibato", "Isandra")
dist.data %>%
  filter(!(district %in% no_data)) -> dist.data
nrow(dist.data)

@@

Applying this framework to our data on reported bites in the Madagascar, we see that estimated rabies incidence exceeds expected incidence in areas with high incidence of reported bites and is lower than expected for areas with little data/low incidence of reported bites (Figure 1).

@@

ordered.bites <- dist.data$avg.bites100k[order(dist.data$study_area)]
par(mar = c(4, 10, 4, 4))
plot(ordered.bites*0.6/0.85, 1:length(ordered.bites), bty = "l", pch = 20, col = "darkred", 
     xlab = "Rabies exposures per 100k persons", ylab = "", axes = FALSE, 
     xlim = c(0, max(ordered.bites*0.6/0.85)+100))
axis(1)
text(dist.data$district[order(dist.data$study_area)], y = 1:length(ordered.bites), x = -10, adj = 1, xpd = TRUE)
points(ordered.bites*0.2/0.85, 1:length(ordered.bites),
       pch = 20, col = "darkred")
segments(y0 = 1:length(ordered.bites), x0 = ordered.bites*0.2/0.85,
         y1 = 1:length(ordered.bites),
         x1 = ordered.bites*0.6/0.85, col = "darkred")
abline(v = c(exps.per100k.high, exps.per100k.low), col = c("red", "red"), lty = 2)
legend("topleft", "Range of expected \n rabies incidence", col = "red", lty = 2, bty = "n",
       inset = c(0.4, 0), xpd = TRUE, x.intersp = 0.2, seg.len = 2)

## Empirical p_report
p_rabid_high <- exps.per100k.high/(dist.data$avg.bites100k)
p_rabid_high[p_rabid_high >= 0.95] <- 0.95
p_rabid_low <- exps.per100k.low/(dist.data$avg.bites100k)
p_rabid_low[p_rabid_low >= 0.95] <- 0.95

plot(dist.data$study_area/60, 
     dist.data$avg.bites100k*p_rabid_high/exps.per100k.high, ylim = c(0, 1), 
     col = "red", pch = 20, bty = "l", xlab = "Travel times (hrs)", ylab = "Reporting")
points(dist.data$study_area/60, 
     dist.data$avg.bites100k*p_rabid_low/exps.per100k.low,  
     col = "darkred")
segments(x0 = dist.data$study_area/60, y0 = dist.data$avg.bites100k*p_rabid_low/exps.per100k.low,
         x1 = dist.data$study_area/60,
         y1 = dist.data$avg.bites100k*p_rabid_high/exps.per100k.high, col = "darkred")
legend("topright", c("High incidence", "Low incidence"), col = c("Red", "darkred"), pch = c(20, 1), 
       bty = "n", inset = c(-0.2, 0), xpd = TRUE)
```

```{r district data}
bites <- dist.data[,6:9]
ttimes <- dist.data$study_area
pop <- dist.data$midpops
times <- 1:4
nlocs <- nrow(dist.data)
exps.high <- exps.per100k.high*dist.data$midpops/1e5
exps.low <- exps.per100k.low*dist.data$midpops/1e5
burn.in = 5000
```

@@

#### Models of reporting by travel time to clinic
To generate more probable estimates of rabies burden given what we know about access to PEP in Maadagascar, we estimate a district specific reporting rate as a function of travel time ($T$) to the nearest ARMC:

$$ \rho_j = logistic(B_{tt}T_j+ B_{0})$$
We can specify our expected bites in a few ways:

##### Given an expected rabies exposures incidence and corresponding $p_{rabid}$:

$$ B_j \sim Poisson(\frac{\rho_j R}{p_{rabid_j}})$$
$$
           p_{rabid_j}=
            \begin{cases}
            x, & \text{if}\ \frac{R_j}{B_j} > x \\
            \frac{R_j}{B_j}, & \text{otherwise}
            \end{cases}
$$

@@

```{r Annual jags model with p_report estimated, echo = FALSE, message = FALSE, results = 'hide'}
## model
tt.model.1 <- "model {
for (j in 1:nlocs){
  for (t in 1:times){
    # Number of bites
    bites[j, t] ~ dpois(rho[j]*expected.mean[j]/p_rabid[j, t])
  }
}

@@

est.p.1 <- function (bites, ttimes, times, nlocs, expected.mean, p_rabid.est){
  p_rabid <- expected.mean/bites
  p_rabid[p_rabid >= p_rabid.est] <- p_rabid.est

  data <- list (bites = bites, times = times,
              expected.mean = expected.mean, p_rabid = p_rabid,
              ttimes = ttimes, nlocs = nlocs)

@@

  jags_mod <- jags.model(textConnection(tt.model.1), data = data, inits = inits, n.chains = 5, 
                       n.adapt = 1000)

  params <- c("B_tt", "B_0")
  samps <- coda.samples(jags_mod, params, n.iter = 10000)
  return(samps)
}
check <- est.p.1(bites = bites, times = times, ttimes = ttimes, nlocs = nlocs,
                        expected.mean = exps.low, p_rabid.est = 0.5)
```

##### Given an expected rabies exposures incidence and non-rabid bites:

$$ B_j \sim Poisson(\rho_j (R_j + N_j))$$
where $N$ is a function of human population size (more people = more people getting bitten by dogs?):
$$ N_j \sim f(pop_j)$$
This assumes that reporting is the same for non-rabid and rabid bites, but that the incidence of non-rabid bites is not uniform across space (as with rabies incidence) and increases with increasing population size.

```{r Annual jags model with p_report estimated, echo = FALSE, message = FALSE, results = 'hide'}
## model
tt.model.2 <- "model {
# reported bites
for (j in 1:nlocs){
  for (t in 1:times){
    # Number of bites
    bites[j, t] ~ dpois(rho[j]*(expected.mean[j] + N[j]))
  }
}

# spatial effects
  for (g in 1:nlocs){
    # Reporting in place g
    logit(rho[g]) <- B_tt*(1/ttimes[g]) + B_0
    # Non-rabid incidence in place g
    log(N[g]) <- B_pop*pop[g] + B_1
  }

# priors
  B_tt ~ dnorm(0, 0.1)
  B_pop ~ dnorm(0, 0.1)
  B_0 ~ dnorm(0, 0.1)
  B_1 ~ dnorm(0, 0.1)
}"

est.p.2 <- function (bites, ttimes, times, pop, nlocs, expected.mean){
  data <- list (bites = bites, times = times, pop = pop,
              expected.mean = expected.mean, p_rabid = p_rabid,
              ttimes = ttimes, nlocs = nlocs)

  inits <- list(B_tt = rnorm(1, 0, 1e-6), 
              B_0 = rnorm(1, 0, 1e-6), B_pop = rnorm(1, 0, 1e-6), 
              B_1 = rnorm(1, 0, 1e-6))

  jags_mod <- jags.model(textConnection(tt.model.2), data = data, inits = inits, n.chains = 5, 
                       n.adapt = 1000)

  params <- c("B_tt", "B_0", "B_1", "B_pop")
  samps <- coda.samples(jags_mod, params, n.iter = 10000)
  return(samps)
}
```

##### Given an expected rabies exposures incidence and reported non-rabid bites:

$$ B_j \sim Poisson(\rho_jR_j + N_j)$$
where $N_j$ is a function of travel time (closer you are to a clinic, higher incidence of reported non-rabid bites):
$$ N_j \sim f(T_j)$$
This assumes that reporting may not be the same for non-rabid and rabid bites, but that the incidence of non-rabid bites increases with travel time, just as reporting increases with travel time. This may be true, but we will likely run into identifiability issues (i.e. estimating two params which increase with travel time, reporting and reported non-rabid incidence).

```{r Annual jags model with p_report estimated, echo = FALSE, message = FALSE, results = 'hide'}
## model
tt.model.3 <- "model {
# reported bites
for (j in 1:nlocs){
  for (t in 1:times){
    # Number of bites
    bites[j, t] ~ dpois(rho[j]*expected.mean[j] + N[j])
  }
}

# spatial effects
  for (g in 1:nlocs){
    # Reporting in place g
    logit(rho[g]) <- B_tt*(1/ttimes[g]) + B_0
    # Non-rabid incidence in place g
    log(N[g]) <- B_nr*(1/ttimes[g]) + B_1
  }

# priors
  B_tt ~ dnorm(0, 0.1)
  B_nr ~ dnorm(0, 0.1)
  B_0 ~ dnorm(0, 0.1)
  B_1 ~ dnorm(0, 0.1)
}"

est.p.3 <- function (bites, ttimes, times, nlocs, expected.mean){
  data <- list (bites = bites, times = times,
              expected.mean = expected.mean,
              ttimes = ttimes, nlocs = nlocs)

  inits <- list(B_tt = rnorm(1, 0, 1e-6), 
              B_0 = rnorm(1, 0, 1e-6), B_nr = rnorm(1, 0, 1e-6), 
              B_1 = rnorm(1, 0, 1e-6))

  jags_mod <- jags.model(textConnection(tt.model.3), data = data, inits = inits, n.chains = 5, 
                       n.adapt = 1000)

  params <- c("B_tt", "B_0", "B_1", "B_nr")
  samps <- coda.samples(jags_mod, params, n.iter = 10000)
  return(samps)
}
```

```{r Annual jags model with p_rabid + p_report estimated, high incidence, echo = FALSE, message = FALSE, results = 'hide'}
## models assuming high incidence

>>>>

``` {r label, out.width = "75%", fig.cap = "Figure 1", echo = FALSE, message = FALSE}
include_graphics("figs/figure2.pdf")

### Preliminary data from the Moramanga District 
* Commune level average travel time to the closest CTAR (generated from global travel time layer from Malaria Atlas Project).
* Human population per commune extracted from World Pop
* 16 months of data on reported animal bites from the Moramanga District in Madagascar 
* In the next month, we will have 4 years of data on reported animal bites from 20 of the 31 CTAR.

```{r setup, echo = FALSE, message = FALSE, results = 'hide'}
## libraries
# for gis 
library(knitr)
# everything else
library(lubridate)
library(reshape2)
library(tidyverse)
library(rjags)
library(coda)
library(lattice)
# pkgs <- c("lattice", "coda")
# require(pkgs, character.only = TRUE)

## gis data {NEED TO FIGURE OUT PROJECTIONS!}
p4s <- "+proj=longlat +datum=WGS84 +no_defs +ellps=WGS84 +towgs84=0,0,0"

## data
exposure.mat <- read.csv("data/exposures_by_commune_Moramanga.csv", header = TRUE, row.names = 1)
moramanga <- readOGR("data/MoramangaGIS/MoramangaPops.shp")
ctar.gps <- read.csv("data/ctar_gps.csv")

## data
monthly.bites <-rowSums(exposure.mat)/ncol(exposure.mat)
moramanga$commune.midpops <- (moramanga$pop2015adj + moramanga$pop2020adj)/2
moramanga$monthly.bites <- monthly.bites[match(moramanga$commune, names(monthly.bites))]
moramanga$monthly.incidence <- moramanga$monthly.bites/moramanga$commune.midpops*1e5

## travel time layer
travel.times <- raster("output/study.area.accessibility.tif")
mora.access <- mask(travel.times, moramanga)
mora.access <- crop(mora.access, moramanga)
moramanga <- raster::extract(mora.access, moramanga, fun = mean, na.rm=TRUE, df = TRUE, sp = TRUE)
moramanga$comm.long <- coordinates(moramanga)[,1]
moramanga$comm.lat <- coordinates(moramanga)[,2]
# # plot it
# plot(mora.access/60,
#      breaks = c(0, 1, 2, 3, 4, 5, 6, 7,8, 16, max(values(mora.access)/60, na.rm = TRUE)),
#      col = c("#fff7f3", "#fde0dd", "#fcc5c0", "#fa9fb5", "#f768a1", "#dd3497", 
#              "#ae017e", "#7a0177", "#49006a"), axes = FALSE, box = FALSE)
# points(moramanga$comm.long[moramanga$commune == "Moramanga"], moramanga$comm.lat[moramanga$commune == "Moramanga"], pch = 18, col = "grey", cex = 2)

@@

Applying this framework to our data on reported bites in the Moramanga District, we see that estimated rabies incidence exceeds expected incidence in areas with high incidence of reported bites and is lower than expected for areas with little data/low incidence of reported bites (Figure 1).

@@

ordered.bites <- moramanga$monthly.incidence[order(moramanga$study.area.accessibility)]*12
par(mar = c(4, 10, 4, 4))
plot(ordered.bites*0.6/0.85, 1:length(monthly.bites), bty = "l", pch = 20, col = "darkred", 
     xlab = "Rabies exposures per 100k persons", ylab = "", axes = FALSE, 
     xlim = c(0, max(ordered.bites*0.6/0.85)+100))
axis(1)
text(moramanga$commune[order(moramanga$study.area.accessibility)], y = 1:length(monthly.bites), x = -10, adj = 1, xpd = TRUE)
points(ordered.bites*0.2/0.85, 1:length(monthly.bites),
       pch = 20, col = "darkred")
segments(y0 = 1:length(monthly.bites), x0 = ordered.bites*0.2/0.85,
         y1 = 1:length(monthly.bites),
         x1 = ordered.bites*0.6/0.85, col = "darkred")
abline(v = c(exps.per100k.high, exps.per100k.low), col = c("red", "red"), lty = 2)
legend("topleft", "Range of expected \n rabies incidence", col = "red", lty = 2, bty = "n",
       inset = c(0.4, 0), xpd = TRUE, x.intersp = 0.2, seg.len = 2)

## Empirical p_report
p_rabid_high <- exps.per100k.high/(moramanga$monthly.incidence*12)
p_rabid_high[p_rabid_high >= 0.95] <- 0.95
p_rabid_low <- exps.per100k.low/(moramanga$monthly.incidence*12)
p_rabid_low[p_rabid_low >= 0.95] <- 0.95

plot(moramanga$study.area.accessibility/60, 
     moramanga$monthly.incidence*12*p_rabid_high/exps.per100k.high, ylim = c(0, 1), 
     col = "red", pch = 20, bty = "l", xlab = "Travel times (hrs)", ylab = "Reporting")
points(moramanga$study.area.accessibility/60, 
     moramanga$monthly.incidence*12*p_rabid_low/exps.per100k.low,  
     col = "darkred")
segments(x0 = moramanga$study.area.accessibility/60, y0 = moramanga$monthly.incidence*12*p_rabid_low/exps.per100k.low,
         x1 = moramanga$study.area.accessibility/60,
         y1 = moramanga$monthly.incidence*12*p_rabid_high/exps.per100k.high, col = "darkred")
legend("topright", c("High incidence", "Low incidence"), col = c("Red", "darkred"), pch = c(20, 1), 
       bty = "n", inset = c(-0.2, 0), xpd = TRUE)

@@

#### Models of reporting by travel time to clinic
To generate more probable estimates of rabies burden given what we know about access to PEP in Maadagascar, we estimate a commune specific reporting rate as a function of travel time ($T$) to the nearest ARMC given an expected rabies exposures incidence and corresponding $p_{rabid}$:

$$ B \sim Poisson(\frac{\rho R}{p_{rabid}})$$
$$ \rho = logistic(B_{tt}T+ B_{0})$$
    $$
           p_{rabid}=
            \begin{cases}
            x, & \text{if}\ \frac{R}{B} > x \\
            \frac{R}{B}, & \text{otherwise}
            \end{cases}
    $$

@@

```{r Annual jags model with p_rabid + p_report estimated, high incidence, echo = FALSE, message = FALSE, results = 'hide'}
## model
tt.model <- "model {
# reported bites
for (j in 1:nlocs){
# Number of bites
  bites[j] ~ dpois(expected.mean[j]*rho[j]/p_rabid[j])
}

@@

est.p <- function (bites, ttimes, nlocs, expected.mean, p_rabid.est){
  p_rabid <- expected.mean/bites
  p_rabid[p_rabid >= p_rabid.est] <- p_rabid.est
  data <- list (bites = bites, 
              expected.mean = expected.mean, p_rabid = p_rabid,
              ttimes = ttimes, nlocs = nlocs)

@@

  params <- c("B_tt", "B_0")
  samps <- coda.samples(jags_mod, params, n.iter = 10000)
  return(samps)
}

bites = round(moramanga$monthly.bites*12)
ttimes = moramanga$study.area.accessibility/60
nlocs = length(moramanga$commune)
exp.low = exps.per100k.low*moramanga$commune.midpops/1e5
exp.high = exps.per100k.high*moramanga$commune.midpops/1e5
burn.in = 5000

### 2018-10-16 archive/accessPEP4.Rmd
Reorganizing files and creating draft rmd to push to googledrive

```{r directory, echo=FALSE, message = FALSE, results = 'hide'}
rm(list = ls())
require("knitr")
opts_knit$set(root.dir = "/Users/mrajeev/Dropbox/MadaPEP")
knitr::opts_chunk$set(fig.pos = 'h')
```
#### Canine rabies
* Annually, an estimated 60,000 people die from canine rabies.
* These deaths are preventable if people receive prompt post-exposure prophylaxis
* In places where rabies is endemic, there are significant barriers to accessing PEP (i.e. socioeconomics, availability)
* In Madagascar, rabies is endemic, however surveillance is poor and little data is available. There are 31 clinics, or CTAR (centre de traitment antirabique), that provide post-exposure prophylaxis in the country (Figure 1).

@@

```{r district data}
bites <- dist.data[,6:9]
ttimes <- dist.data$study_area
pop <- dist.data$midpops
times <- 1:4
nlocs <- nrow(dist.data)
exps.high <- exps.per100k.high*dist.data$midpops/1e5
exps.low <- exps.per100k.low*dist.data$midpops/1e5
burn.in = 5000
```

@@

# spatial effects
  for (g in 1:nlocs){
    # Reporting in place g
    logit(rho[g]) <- B_tt*(1/ttimes[g]) + B_0
    # Non-rabid incidence in place g
    log(N[g]) <- B_pop*pop[g] + B_1
  }

@@

est.p.2 <- function (bites, ttimes, times, pop, nlocs, expected.mean){
  data <- list (bites = bites, times = times, pop = pop,
              expected.mean = expected.mean, p_rabid = p_rabid,
              ttimes = ttimes, nlocs = nlocs)

@@

  params <- c("B_tt", "B_0", "B_1", "B_pop")
  samps <- coda.samples(jags_mod, params, n.iter = 10000)
  return(samps)
}
```

>>>>

```{r directory, echo=FALSE, message = FALSE, results = 'hide'}
rm(list = ls())
require("knitr")
knitr::opts_chunk$set(fig.pos = 'h')
```
#### Canine rabies
* Annually, an estimated 60,000 people die from canine rabies.
* These deaths are preventable if people receive prompt post-exposure prophylaxis
* In places where rabies is endemic, there are significant barriers to accessing PEP (i.e. socioeconomics, availability)
* In Madagascar, rabies is endemic, however surveillance is poor and little data is available. There are 31 clinics, or CTAR (centre de traitment antirabique), that provide post-exposure prophylaxis in the country (Figure 1).

@@

```{r district data}
bites <- dist.data[,6:9]
ttimes <- dist.data$study_area
pop <- dist.data$midpops
times <- ncol(bites)
nlocs <- nrow(bites)
exps.high <- exps.per100k.high*dist.data$midpops/1e5
exps.low <- exps.per100k.low*dist.data$midpops/1e5
burn.in = 5000
```

@@

# spatial effects
  for (g in 1:nlocs){
    # Reporting in place g
    logit(rho[g]) <- B_tt*(1/ttimes[g]) + B_0

    # Non-rabid incidence in place g
    log(N[g]) <- B_pop*pop[g] + B_1
  }

@@

est.p.2 <- function (bites, ttimes, times, pop, nlocs, expected.mean){
  data <- list (bites = bites, times = times, pop = pop,
              expected.mean = expected.mean,
              ttimes = ttimes, nlocs = nlocs)

@@

  params <- c("B_tt", "B_0", "B_1", "B_pop")
  samps <- coda.samples(jags_mod, params, n.iter = 10000)
  return(samps)
}

check <- est.p.2(bites = bites, times = times, ttimes = ttimes, pop = pop, nlocs = nlocs,
                        expected.mean = exps.high)
plot(check)
gelman.diag(check)
check <- summary(window(check, start = burn.in))
ttimes.plot <- seq(0.01, 12, by = 0.2)*60
par(mar = c(2,2,2,2))
plot(ttimes.plot,
     plogis(check$statistics[,"Mean"]["B_tt"]*(1/ttimes.plot)
                  + check$statistics[,"Mean"]["B_0"]),
     type = "l", col = "slateblue1")
